A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-01 paper.tex
Change paper structures

\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

@@

\section{Background}
\label{section:background}
In this section, we review Ethereum Smart Contract, MAM, the architecture and workflow of decentralized data marketplace.

\subsection{Ethereum Smart Contract}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.

\subsection{Masked Authenticated Messaging}
MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.

@@

\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others. In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

@@

\section{Related Work}
\label{section:relatedWork}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

>>>>

@@

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchangement mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

\subsection{Decentralized Data Marketplace Infrastructure}
% decentralized DM

\subsection{Distributed Storage System}
% distributed data storage
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

\section{System Design Thinking}
\subsection{The Architecture}
% TODO: pub/sub model selection
% use IPFS as searching indexes
\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

% MAM
MAM publishes authenticated streaming data as zero-value transactions to IOTA ledger and provides the ability to publish and fetch encrypted messages over the IOTA Tangle along with data integrity and access control. With MAM, the rights of data access are traded instead of a copy of data in the data marketplace, which eliminates the need for data consumers to have additional storage.

@@

% alternative solution => IPFS(data) + MAM(index)

\subsection{Enable Automated Trading Process}
% Ethereum Smart Contract
% use ethereum smart contract => IOTA smart contracts are still under development
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. 
It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it will be executed automatically without any third-parties and it is uninterruptible.

\section{Decentralized Data Marketplace Case Study}
\subsection{Participants in Decentralized Data Marketplace}
There are three major roles, data providers, data consumers and brokers in the decentralized data marketplace which is similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others. In our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. Fig.~\ref{fig:system_design}

@@
